\documentclass{report}

\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{SPL}{%
	alsoletter={0123456789ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz_+-*/\%=<>!\&|}
	morekeywords={while,else,if,print,return,isEmpty,fst,snd,hd,tl,Int,Char,Bool,Void,True,False,var},%
	sensitive=true,%
	morecomment=[l]{//},%
	morecomment=[n]{/*}{*/},%
	literate=%
		{->}{{$\rightarrow$}}2
		{>=}{{$\geq\:$}}1
		{<=}{{$\leq\:$}}1
		{==}{{$\equiv$}}1
}
\lstset{%
	upquote=true,
	breakatwhitespace=false,
	breaklines=true,
	postbreak=\mbox{\textcolor{gray}{$\hookrightarrow$}\space},
	keepspaces=true,
	basicstyle=\tt\footnotesize,
	commentstyle=\sl,
	keywordstyle=\bf,
	stringstyle=\tt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=4,
	basewidth=0.43em,
	columns=[c]fixed,
	texcl=true,
	captionpos=b
}

\author{%
	Sjaak~Smetsers\\
	\small\texttt{s123456}\and
	Mart~Lubbers\\
	\small\texttt{s123456}
}
\date{\today}
\title{My compiler}

\begin{document}

\maketitle%

\tableofcontents%

\chapter{Introduction}
\begin{quote}
	\it
	This document is a mandatory skeleton for your report.
	It gives by no means an exhaustive list of suggestions for content.
	The report should be readable self-contained and readable without access to the source code.
\end{quote}
\begin{itemize}
	\item Motivate your language choice
	\item Introduce spl
	\item Give some nice examples.
	\item \ldots
\end{itemize}

\chapter{Lexing \& Parsing}
\begin{itemize}
	\item How did you design the Abstract Syntax Tree
	\item How does the parser work?
	\item How did you handle difficult things like fixity, associativity etc.
	\item Is there error handling? Recovery?
	\item Do you have a lexer and parser?
	\item How do they communicate?
	\item Problems?
	\item\ldots
\end{itemize}

\chapter{Analyses \& Typing}
\begin{itemize}
	\item New Abstract Syntax Tree? Decorate existing Abstract Syntax Tree?
	\item Error messages?
	\item Polymorphism? Inference? Overloading?
	\item Problems?
	\item\ldots
\end{itemize}

\chapter{Code Generation}
\begin{itemize}
	\item Compilation scheme?
	\item How is data represented? Lists tuples
	\item Semantics style, call-by-reference, call-by-value?
	\item How did you solve overloaded functions?
	\item Polymorphism?
	\item Printing?
	\item Problems?
	\item\ldots
\end{itemize}

\chapter{Extension}
Describe your extension in detail

\chapter{Conclusion}
What does work, what does not etc.

\section{Reflection}
\begin{itemize}
	\item What do you think of the project?
	\item How did it work out?
	\item How did you divide the work?
	\item Pitfalls?
	\item \ldots
\end{itemize}

\appendix
\chapter{Grammar}
Change the grammar to the one you actually used

\begin{verbatim}
SPL       = Decl+
Decl      = VarDecl
          | FunDecl
VarDecl   = ('var' | Type) id  '=' Exp ';'
FunDecl   = id '(' [ FArgs ] ')' [ '::' FunType ] '{' VarDecl* Stmt+ '}'
RetType   = Type
          | 'Void'
FunType   = [ FTypes ] '->' RetType
FTypes    = Type [ FTypes ]
Type      = BasicType
          | '(' Type ',' Type ')'
          | '[' Type ']'
          | id
BasicType = 'Int'
          | 'Bool'
          | 'Char'
FArgs     = [ FArgs ',' ] id
Stmt      = 'if' '(' Exp ')' '{' Stmt* '}' [ 'else' '{' Stmt* '}' ]
          | 'while' '(' Exp ')' '{' Stmt* '}'
          | id Field '=' Exp ';'
          | FunCall ';'
          | 'return' [ Exp ] ';'
Exp       = id Field
          | Exp Op2 Exp
          | Op1 Exp
          | int
          | char
          | 'False' | 'True'
          | '(' Exp ')'
          | FunCall
          | '[]'
          | '(' Exp ',' Exp ')'
Field     = [ Field ( '.' 'hd' | '.' 'tl' | '.' 'fst' | '.' 'snd' ) ]
FunCall   = id '(' [ ActArgs ] ')'
ActArgs   = Exp [ ',' ActArgs ]
Op2       = '+'  | '-' | '*' | '/'  | '%'
          | '==' | '<' | '>' | '<=' | '>=' | '!='
          | '&&' | '||'
          | ':'
Op1       = '!'  | '-'
int       = [ '-' ] digit+
id        = alpha ( '_' | alphaNum)*
\end{verbatim}

\end{document}
